cardinalR: Generating interesting high-dimensional data structures

### 2025-11-19 paper-cardinalR.Rmd
Updated application intro

This section demonstrates how the package can be used to generate complex high-dimensional datasets, apply dimension reduction (DR) techniques, and evaluate clustering performance. The example shows how diverse geometric structures can be simulated and analyzed to assess algorithmic behavior.

>>>>

This section demonstrates how the package can be used to generate complex high-dimensional datasets, evaluate dimension reduction (DR) and clustering methods. The example shows how diverse geometric structures can be simulated and analyzed to assess algorithmic behavior.
